Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-11 automatica/paper.tex
results

We separate our evaluation into two sets of results: fixed- and floating-point. 
%For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
%back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
%from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
%(14) than the multi-staged back-end (13)}.
%%\note{we should clarify that this is out of 26 in total, not 191?}  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 53\% of the time required using the multi-staged
%back-end, and has a median run-time 0.5\,s, which is twenty times smaller
%than the multi-staged approach.  The two back-ends complement each other in terms of 
%benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%%
%For the majority of the benchmarks with {\it floating-point} implementation, 
%we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
%but both back-ends find the same amount of solutions (13).  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 50\% of the time required using the multi-staged
%back-end, and has a median run-time 0.6\,s, which is forty times smaller
%than the multi-staged approach.  The two back-ends complement each other in
%benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 67.6\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

The median run-time for \textcolor{blue}{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

\textcolor{blue}{We fail to synthesise a controller for several instances.}  
For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout. 
A controller simply may not exist for these benchmarks at this given time discretisation and controller
precision.  
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.

>>>>

We separate our evaluation into two sets of results: fixed- and floating-point. 
We are able to synthesise more floating point controllers than fixed point controllers, likely because the
floating point controllers are at a higher precision than the fixed point. It may be that the precision of the fixed-point
controllers is too low to be able to meet the safety specification. The floating point controllers take longer to synthesise
than the fixed point controllers.
%For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
%back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
%from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
%(14) than the multi-staged back-end (13)}.
%%\note{we should clarify that this is out of 26 in total, not 191?}  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 53\% of the time required using the multi-staged
%back-end, and has a median run-time 0.5\,s, which is twenty times smaller
%than the multi-staged approach.  The two back-ends complement each other in terms of 
%benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%%
%For the majority of the benchmarks with {\it floating-point} implementation, 
%we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
%but both back-ends find the same amount of solutions (13).  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 50\% of the time required using the multi-staged
%back-end, and has a median run-time 0.6\,s, which is forty times smaller
%than the multi-staged approach.  The two back-ends complement each other in
%benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

@@

\begin{table*}
\centering
\begin{tabular}{| l | c | c | r | c | r |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
%1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
 Antenna     & 6 &  & ~\xmark & 16,10 & 817.4\,s \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
 Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &23.6\,s \\
 Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.7\,s \\
%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
 Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s \\
 CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s  \\
 Cstr & 3 & & ~\xmark & 16,10 & 21.4\,s \\
 Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 15.4\,s \\
 DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
 Helicopter   & 3 &  & ~\xmark & 16,10 & 32.0\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Invpendulum\_pendang & 2 & 16,8  & 10.7 & 16,10 & 14.8\,s\\
 Magpointer   & 2 &  & ~\xmark & 16,10 & 86.0\,s \\
 Magsuspension  & 2 & 12,12  & 39.0\,s  & 16,10 & 43.2\,s \\
 Pendulum   & 2 & 16,8 & 13.2\,s & 16,10 & 16.6\,s\\
 Regulator   & 5 & 16,8 & 1532.7\,s & 16,10 & 999.6\,s\\
 Springmassdamper & 2 & & ~\xmark &16,10 & 24.2s \\
 Steamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
 Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
 Tapedriver   & 3 & 16,8  & 11.4\,s &16,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

The mean run-time for \textcolor{blue}{the successful} benchmarks is 152.6\,s for the fixed-point and 117.5\,s for floating-point implementations, respectively.  The mean run-time for \textcolor{blue}{the successful} benchmarks is 16\,s for the fixed-point and 11\,s for floating-point implementations, respectively.
We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

\textcolor{blue}{We fail to synthesise a controller for several instances.}  
The completeness threshold may be too large, thus causing a timeout, or controller simply may not exist for these benchmarks at this given time discretisation and controller
precision.
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.
